Quantifying the home ground advantage with `hyper2` and `hyper3` objects

### 2025-02-08 inst/home_advantage.Rmd
weight comparison work of Davidson and Beaver

>>>>

### Analysis of  Work by Davidson and Beaver

```{r}
DB <- # Davidson and Beaver
matrix(c(
    NA, 32+18i, 36+14i, 47+03i, 47+03i,
14+36i,     NA, 34+16i, 43+07i, 46+04i,
06+44i, 14+36i,     NA, 34+16i, 40+10i,
02+48i, 07+43i, 12+38i,     NA, 28+22i,
01+49i, 02+48i, 05+45i, 10+40i,     NA
),5,5,byrow=TRUE
)
jj <- c("90g","95g","100g","105g","110g")
dimnames(DB) <- list(`@home` = jj, `@away` = jj)
DB
```

```{r first_second_likefun, cache=TRUE}
f <- function(l){ maxp(home_away3(DB,l),give=TRUE,n=1)$likes}
lam <- seq(from=0.6,to=1,len=19)
date()
loglike <- sapply(lam,f)
date()
```

```{r plotfirstsecond}
plot(lam,loglike-max(loglike),type='b')
abline(h=c(0,-2))
abline(v=1)
```
